---
title: "Developing Data Products Final Project - Reproducible Pitch"
author: "Ashwin Sai Murali Neelakandan"
date: "2024-12-01"
output: 
  ioslides_presentation: 
    keep_md: true
    widescreen: true
    fig_width: 8
    fig_height: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background  

This presentation is created using R markdown in RStudio as a pitch for the Shiny app that can be found at  
https://ashwinnagasai.shinyapps.io/Developing_Data_Products_Final_Project/   

The app uses linear regression to predict Fertility using  Agriculture and Education as the predictors  

The Shiny App Source code is available at https://github.com/AshwinNagasai/Developing-Data-Products

## Data  

Swiss Fertility data with standardized fertility measure and socioeconomic indicators for each of 47 French-speaking provinces of Switzerland at 1888. The data frame has 47 observations with 6 variables, the variables considered are   

- Fertility (Ig) - common standardized fertility measure  
- Agriculture - % of males involved in agriculture as occupation  
- Education - % education beyond primary school for draftees  
   
```{r, echo = FALSE}
# Looking at the data set
head(swiss, 3)
```

## R Code for Plot


```{r, echo=TRUE, message=FALSE}
library(ggplot2)
library(plotly)
g <- ggplot(data = swiss, aes(Agriculture, Fertility), 
            xlab("Agriculture"), 
            ylab("Fertility"))
g = g + geom_point(size = 5, color = "blue", alpha = 0.2)
g = g + geom_point(size = 5, color = "red", alpha = 0.2) 
g = g + geom_smooth(method = lm, color = "grey0")
finalplot <- ggplotly(g)
```

## Regression Model - Fertility Vs Agriculture

```{r, fig.align='center'}
finalplot
```  
